---
title: "Gentrification Patdown CD4 Smith Skeen MGMT"
author: "Ethan A. Smith"
date: "2026-06-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(haven)
require(tidygeocoder)
require(tidyverse)
require(sf)
require(sp)
require(readr)
require(stringr)
require(tidycensus)
library(psych)
library(gtsummary)
library(lme4)  
library(car)   

```

## Methods 

#Design
We tested these hypotheses via a secondary cross-sectional analysis of baseline (BL) New Orleans Alcohol Use in HIV (NOAH) cohort data [51], geocoded and linked to aggregate areal SES indices derived from American Community Survey (ACS) estimates [52]. Exploratory factor analysis detected latent subconstructs of urban life stress, which were modeled as predictors of suboptimal CD4 T-cell count and aggravators of depressive symptomatology, via 2-level logit and multivariable OLS regression modeling, respectively.

```{r Pull NOAH, ACS,}

noah <- read_sas("C:/Users/Ethan/Box/nola-gem/Data/Baseline Data/noah_baseline365_scored.sas7bdat")

#Concatenate into single address variable 
noah$full_address <- paste(noah$street_address, noah$city, noah$state, noah$zipcode, sep = ", ")

noah_tst <- noah %>% 
  geocode(address = full_address, method = 'arcgis')

#patdowns

df_2018 <- read.csv("C:/Users/Ethan/Desktop/SBM_abstract/Raw Data/df_18.csv")

df_2018 <- df_2018 %>%
  mutate(patdown = ifelse(grepl("Search Occurred: Yes;Search Types: Pat-down;|Pat down: Yes", ActionsTaken), 1, 0),
         drugs = ifelse(grepl("Drugs", ActionsTaken), 1, 0),
         surplus = ifelse(grepl("No action taken", ActionsTaken), 1, 0),
         citation = ifelse(grepl("Citation Issued", ActionsTaken), 1, 0),
         arrest = ifelse(grepl("Physical Arrest", ActionsTaken), 1, 0),
    patdown_wht = ifelse(grepl("Search Occurred: Yes;Search Types: Pat-down;|Pat down: Yes", ActionsTaken) & SubjectRace == "WHITE", 1, 0),
    drugs_wht = ifelse(grepl("Drugs", ActionsTaken) & SubjectRace == "WHITE", 1, 0),
    surplus_wht = ifelse(grepl("No action taken", ActionsTaken) & SubjectRace == "WHITE", 1, 0),
    citation_wht = ifelse(grepl("Citation Issued", ActionsTaken) & SubjectRace == "WHITE", 1, 0),
    arrest_wht = ifelse(grepl("Physical Arrest", ActionsTaken) & SubjectRace == "WHITE", 1, 0),
    patdown_blk = ifelse(grepl("Search Occurred: Yes;Search Types: Pat-down;|Pat down: Yes", ActionsTaken) & SubjectRace == "BLACK", 1, 0),
    drugs_blk = ifelse(grepl("Drugs", ActionsTaken) & SubjectRace == "BLACK", 1, 0),
    surplus_blk = ifelse(grepl("No action taken", ActionsTaken) & SubjectRace == "BLACK", 1, 0),
    citation_blk = ifelse(grepl("Citation Issued", ActionsTaken) & SubjectRace == "BLACK", 1, 0),
    arrest_blk = ifelse(grepl("Physical Arrest", ActionsTaken) & SubjectRace == "BLACK", 1, 0)
  )


```

# Measures 
Our level-2 exposure of interest, the Index of Concentration at the Extremes (ICE), was calculated at the CT level using 2010–2015 ACS pooled 5-year estimates. Guided by Krieger [53], the sum of non-Hispanic (NH) White families whose annual household income was ≥80th percentile (≥$100,000) minus the sum of NH Black families whose household income <20th percentile (<$25,000), was divided by the total population in the CT with known income [53]. The ICE is a versatile and well-established measure of racially polarized SES, robust against the small-sample biases that can distort the Gini coefficient at lower levels of geography [54].


```{r gentrification prep}

####################  Census ###################################################

## 2.1 2006-2010 ACS ----
census_2010 <- get_acs(
  variables = c(
    med_rent = "B25064_001",      # median rent
    med_home_val = "B25077_001",  # median home value, owner-occupied
    med_hhinc = "B19013_001",     # median household income (2010 inflation-adjusted)
    pop = "B01001_001",           # total population
    pop25 = "B15002_001",         # population over 25
    edu1a = "B15002_015",         # male, has bachelor's degree
    edu2a = "B15002_016",         # male, has master's degree
    edu3a = "B15002_017",         # male, has professional degree
    edu4a = "B15002_018",         # male, has doctorate
    edu1b = "B15002_032",         # female, has bachelor's degree
    edu2b = "B15002_033",         # female, has master's degree
    edu3b = "B15002_034",         # female, has professional degree
    edu4b = "B15002_035",         # female, has doctorate
    white = "B03002_003",         # race/eth, non-hispanic white
    black = "B03002_004",         # race/eth, non-hispanic black
    latinx = "B03002_012"         # race/eth, latinx
  ),
  geography = "tract", 
  state = "LA", 
  county = "Orleans", 
  survey = "acs5",
  year = 2010
) 
## ! note: tract-level variables are only in five-year estimate files
## https://www.census.gov/content/dam/Census/library/publications/2020/acs/acs_geography_handbook_2020_ch01.pdf

# format to wide 
census10 <- pivot_wider(
  data = census_2010, 
  id_cols = c(GEOID, NAME), 
  names_from = variable, 
  values_from = estimate
) %>%
  # create tract-level % with at least a bachelor's degree
  mutate(
    # % black
    pct_black = black / pop,
    # % latinx
    pct_latinx = latinx / pop,
    # % white
    pct_white = white / pop,
    # total with a bachelor's
    tot_edu = dplyr::select(.,edu1a:edu4b) %>% rowSums(),
    # proportion with a bachelor's
    pct_edu = ifelse(tot_edu == 0, 0, tot_edu / pop25),
    # low income indicator, at or below median
    low_inc10 = ifelse(med_hhinc > median(med_hhinc, na.rm = TRUE), 0, 1)
  ) %>% 
  # rename variables for merging
  rename(
    med_hhinc10 = med_hhinc,
    med_rent10 = med_rent,
    med_home_val10 = med_home_val,
    pct_edu10 = pct_edu
  )



# https://api.census.gov/data/2018/acs/acs5/variables.html
census_2018 <- get_acs(
  variables = c(
    med_rent = "B25064_001",      # median rent
    med_home_val = "B25077_001",  # median home value, owner-occupied
    households_white = "B19001A_001",
    households_blk = "B19001B_001",
    households = "B19001_001",
    med_hhinc = "B19013_001",     # median household income (2019 inflation-adjusted)
    pop = "B01001_001",           # total population
    pop25 = "B15002_001",         # population over 25
    edu1a = "B15002_015",         # male, has bachelor's degree
    edu2a = "B15002_016",         # male, has master's degree
    edu3a = "B15002_017",         # male, has professional degree
    edu4a = "B15002_018",         # male, has doctorate
    edu1b = "B15002_032",         # female, has bachelor's degree
    edu2b = "B15002_033",         # female, has master's degree
    edu3b = "B15002_034",         # female, has professional degree
    edu4b = "B15002_035",         # female, has doctorate
    white = "B03002_003",         # race/eth, non-hispanic white
    black = "B03002_004",         # race/eth, non-hispanic black
    latinx = "B03002_012",         # race/eth, latinx
    whiteinc14 = "B19001H_014",   # White HH: $100K to $124K
    whiteinc15 = "B19001H_015",   # White, higher incomes
    whiteinc16 = "B19001H_016",   # White, higher incomes
    whiteinc17 = "B19001H_017",   # B19001H_015E-17E White, higher incomes
    blackinc5 = "B19001B_005",    #  Black HH:  $20k-25k
    blackinc2 = "B19001B_002",    # Black lower incomes
    blackinc3 = "B19001B_003",    # Black lower incomes
    blackinc4 = "B19001B_004"     # B19001B_002E-4E Black lower incomes
  ),
  geography = "tract", 
  state = "LA", 
  county = "Orleans", 
  survey = "acs5",
  year = 2018
  #,geometry = TRUE
)

## format to wide 
census18 <- pivot_wider(
  data = census_2018, 
  id_cols = c(GEOID, NAME), 
  names_from = variable, 
  values_from = estimate
) %>%
  # create tract-level % with at least a bachelor's degree
  mutate(
    # % black
    pct_black = black / pop,
    # % latinx
    pct_latinx = latinx / pop,
    # % white
    pct_white = white / pop,
    # total with a bachelor's
    tot_edu = dplyr::select(.,edu1a:edu4b) %>% rowSums(),
    # proportion with a bachelor's
    pct_edu = ifelse(tot_edu == 0, 0, tot_edu / pop25),
    # ICE Race & Income
    ice_race_inc = ((whiteinc14+whiteinc15+whiteinc16+whiteinc17)-(blackinc5+blackinc2+blackinc3+blackinc4))/
      households,
    # ICE Race
    ice_race = (white-black)/pop
  )

## merge 2010 with 2018 ACS ----
gen_data18 <- census18 %>%
  # add relevant 2010 tract-level variables
  left_join(
    census10[, c(
      "GEOID","low_inc10","med_hhinc10","med_rent10",
      "med_home_val10","pct_edu10"
    )], 
    by = "GEOID"
  ) %>%
  mutate(
    # tract-level percent change from 2010 to 2018
    diff_rent = (med_rent - med_rent10) / med_rent10,
    diff_home_val = (med_home_val - med_home_val10) / med_home_val10,
    ## ! note: using absolute change in % with bachelor's due to 0 values in 2010
    diff_pct_edu = pct_edu - pct_edu10,
    # city-wide median percent differences from 2010 to 2018
    c_diff_rent = (
      median(med_rent, na.rm = TRUE) - median(med_rent10, na.rm = TRUE)
    ) / median(med_rent10, na.rm = TRUE),
    c_diff_home_val = (
      median(med_home_val, na.rm = TRUE) - median(med_home_val10, na.rm = TRUE)
    ) / median(med_home_val10, na.rm = TRUE),
    ## ! note: using absolute change in % with bachelor's due to 0 values in 2010
    c_diff_pct_edu = median(pct_edu, na.rm = TRUE) - median(pct_edu10, na.rm = TRUE),
    # gentrification indicator
    gen_cat18 = ifelse(
      # 0 = non-gentrifiable
      low_inc10 == 0, 0, ifelse(
        # 2 = gentrifying
        low_inc10 == 1 & 
          ((diff_rent > c_diff_rent) | (diff_home_val > c_diff_home_val)) &
          (diff_pct_edu > c_diff_pct_edu),
        # otherwise, 1 = gentrifiable
        2, 1
      )
    ) %>% as.factor()
  )




```

```{r patdown and VC calculation}

#Get blank shapefile for Census
census_2018 <- get_acs(
  variables = c( pop = "B01001_001"),
  geography = "tract", 
  state = "LA", 
  county = "Orleans", 
  survey = "acs5",
  year = 2018,
  geometry = TRUE
) 


############################Patdowns ###########################################


# Convert to spatial data
df_sf <- st_as_sf(df_2018, coords = c("Longitude", "Latitude"), crs = 4326)

census_2018 <- st_transform(census_2018, 3452)
df_sf <- st_transform(df_sf, st_crs(census_2018))

# Spatial join
joined_data <- st_join(df_sf, census_2018)

counts <- joined_data %>%
  group_by(GEOID) %>%
  dplyr::summarize(
    drugs_count = sum(drugs, na.rm = TRUE),
    arrest_count = sum(arrest, na.rm = TRUE),
    surplus_count = sum(surplus, na.rm = TRUE),
    citation_count = sum(citation, na.rm = TRUE),
    patdown_count = sum(patdown, na.rm = TRUE),
    drugs_wht_count = sum(drugs_wht, na.rm = TRUE),
    drugs_blk_count = sum(drugs_blk, na.rm = TRUE),
    arrest_wht_count = sum(arrest_wht, na.rm = TRUE),
    arrest_blk_count = sum(arrest_blk, na.rm = TRUE),
    surplus_wht_count = sum(surplus_wht, na.rm = TRUE),
    surplus_blk_count = sum(surplus_blk, na.rm = TRUE),
    citation_wht_count = sum(citation_wht, na.rm = TRUE),
    citation_blk_count = sum(citation_blk, na.rm = TRUE),
    patdown_wht_count = sum(patdown_wht, na.rm = TRUE),
    patdown_blk_count = sum(patdown_blk, na.rm = TRUE)
  )

# Merge counts with census data
final_data <- left_join(gen_data18, counts, by = "GEOID")


################################ Violent Crime #################################

calls2018_conf <- read.csv("C:/Users/Ethan/Desktop/SBM_abstract/911_2018_conf.csv")

#Confirmed
calls2018_conf <- calls2018_conf[!is.na(calls2018_conf$Longitude) & !is.na(calls2018_conf$Latitude), ]
calls_conf_sf <- st_as_sf(calls2018_conf, coords = c("Longitude", "Latitude"), crs = 4326)

calls_conf_sf <- st_transform(calls_conf_sf, st_crs(census_2018))
joined_data_911_conf <- st_join(calls_conf_sf, census_2018)

counts_911_conf <- joined_data_911_conf %>%
  group_by(GEOID) %>%
  dplyr::summarize(
    dv_conf_count = sum(DV, na.rm = TRUE),
    Homicide_conf_count = sum(Homicide, na.rm = TRUE),
    Robbery_conf_count = sum(Robbery, na.rm = TRUE),
    Weapon_conf_count = sum(Weapon, na.rm = TRUE),
    Assault_conf_count = sum(Assault, na.rm = TRUE),
    ViolentCrime_conf_count = sum(ViolentCrime, na.rm = TRUE),
    ShotsFired_conf_count = sum(ShotsFired, na.rm = TRUE),
    drugs_911_conf_count = sum(drugs_911, na.rm = TRUE),
  )

#sum(counts_911_all$ShotsFired_count)
#sum(counts_911_conf$ShotsFired_conf_count)


final_data <- left_join(final_data, counts_911_conf, by = "GEOID")


```

# Participants and Procedures
NOAH, a translational prospective cohort study, aimed to advance knowledge on environmental and biopsychosocial mediators of the effects of alcohol use on HIV-related comorbidity, disease progression, and processes of aging, among virally suppressed PLWH [51]. Participants (N = 365) aged ≥18 years were enrolled via outpatient HIV clinics across the Greater New Orleans, Louisiana metropolitan area from October 2015 to October 2017. Clinic patients who demonstrated potentially hazardous patterns of alcohol use, scoring ≥8 on the Alcohol Use Disorders Identification Test (AUDIT), were oversampled at a 1:1 ratio. Patients with a past-6-week acute illnesses, nonprophylaxis antibiotic prescription, or pregnancy, were excluded. Comprehensive biopsychosocial assessments were undertaken at BL appointments administered at the Louisiana State University Health Sciences Center Clinical and Translational Research Center. Biospecimen collection was conducted under overnight fasting conditions. Survey measures were administered by trained research staff and recorded in REDCap. EHR data were abstracted and migrated to REDCap as an adjacent study form. A detailed protocol of NOAH BL data collection procedures is provided in Appendix S1 of Welsh et al. [51]. 
	As our scope of inquiry was focused on metropolitan New Orleans, the broader NOAH sample was restricted to n = 335 participants who resided in Orleans and surrounding parishes.




```{r cleaning NOAH Data}


noah_filt <- noah_tst %>%
  filter(str_detect(city, regex("new[ _]*orleans", ignore_case = TRUE)) |  city == "Algiers")


# Plot each address, pull out only coordinates and study ID  
noah_geo <- noah_filt %>% dplyr::select(lat, long, carc_study_id) 

# Map coordinates 
noah_geo <- noah_geo %>%
  filter(!is.na(long) & !is.na(lat))

noah_geo <- st_as_sf(noah_geo, coords = c("long", "lat"), crs = 4326)
noah_geo <- st_transform(noah_geo, 3452)
crs(noah_geo)
# Create buffers around each address

noah_geo_0_10_mile <- st_buffer(noah_geo, dist = 0.10 * 5280)  # 0.10 miles
noah_geo_0_25_mile <- st_buffer(noah_geo, dist = 0.25 * 5280)  # 0.25 miles
noah_geo_0_50_mile <- st_buffer(noah_geo, dist = 0.50 * 5280)  # 0.50 miles

# Spatial join our buffers to each exposure

process_noah_geo <- function(calls_data, buffer_data) {
  # Get unique carc_study_ids
  buffer_ids <- buffer_data %>%
    st_drop_geometry() %>%
    distinct(carc_study_id)
  
  # Perform spatial join
  joined_data <- st_join(calls_data, buffer_data, join = st_intersects)
  
  # Aggregate incident count
  aggregated_data <- joined_data %>%
    group_by(carc_study_id) %>%
    summarise(incident_count = n(), .groups = 'drop') %>%
    st_drop_geometry()
  
  # fill in 0 for no intersections
  final_data <- buffer_ids %>%
    left_join(aggregated_data, by = "carc_study_id") %>%
    mutate(incident_count = ifelse(is.na(incident_count), 0, incident_count))
  
  return(final_data)
}

calls_conf_sf <- calls_conf_sf %>% filter(ViolentCrime == 1)

noah_geo_0_10_agg <- process_noah_geo(calls_conf_sf, noah_geo_0_10_mile)
noah_geo_0_25_agg <- process_noah_geo(calls_conf_sf, noah_geo_0_25_mile)
noah_geo_0_50_agg <- process_noah_geo(calls_conf_sf, noah_geo_0_50_mile)

# Join these back to our NOAH Dataset (it wouldn't let me pipe the rename off the left join)

noah_filt <- left_join(noah_filt, noah_geo_0_10_agg, by = "carc_study_id") 
noah_filt <- noah_filt %>% rename(vc_call_010m = incident_count)

noah_filt <- left_join(noah_filt, noah_geo_0_25_agg, by = "carc_study_id")
noah_filt <- noah_filt %>% rename(vc_call_025m = incident_count)

noah_filt <- left_join(noah_filt, noah_geo_0_50_agg, by = "carc_study_id")
noah_filt <- noah_filt %>% rename(vc_call_050m = incident_count)

# Filter data for patdowns
patdown <- df_sf %>% filter(patdown == 1)

# Spatial join and aggregate for patdowns
noah_geo_0_10_agg_pat <- process_noah_geo(patdown, noah_geo_0_10_mile)
noah_geo_0_25_agg_pat <- process_noah_geo(patdown, noah_geo_0_25_mile)
noah_geo_0_50_agg_pat <- process_noah_geo(patdown, noah_geo_0_50_mile)

# Join these back to the NOAH dataset
noah_filt <- left_join(noah_filt, noah_geo_0_10_agg_pat, by = "carc_study_id") 
noah_filt <- noah_filt %>% rename(pd_call_010m = incident_count)

noah_filt <- left_join(noah_filt, noah_geo_0_25_agg_pat, by = "carc_study_id")
noah_filt <- noah_filt %>% rename(pd_call_025m = incident_count)

noah_filt <- left_join(noah_filt, noah_geo_0_50_agg_pat, by = "carc_study_id")
noah_filt <- noah_filt %>% rename(pd_call_050m = incident_count)

# Now NOAH Data have buffer exposures, we will now join to census tract 

noah_geoid <- st_join(noah_geo, census_2018, join = st_intersects)
noah_geoid <- noah_geoid %>% dplyr::select(carc_study_id, GEOID) %>% st_drop_geometry()


noah_filt <- left_join(noah_filt, noah_geoid, by = "carc_study_id")
noah_filt <- left_join(noah_filt, final_data, by = "GEOID")



```

	Our level-1 exposures of interest relied on the 21-item Urban Life Stressor Scale (ULSS), which taps the acuity of a range of urban environmental stressors, e.g. parenting, housing circumstances, the availability of transportation and public services, inter-racial discord, and relations with law enforcement. The ULSS is scored on a 5-point scale, anchored at 1 = “No stress at all” and 5 = “Extremely stressful – more than I can handle” [55].

Individual Items:
  "ul21", = police
  "ul13", = Crime and violence
  "USER_ulss7",  = Your neighborhood environment
  "USER_ulss1",  = Money or finances
  
```{r ULSS}

# Calculate sum and average for `ulss21`
noah_filt <- noah_filt %>%
  mutate(
    ulss_sum = rowSums(dplyr::select(., starts_with("ulss")), na.rm = TRUE),
    ulss_avg = rowMeans(dplyr::select(., starts_with("ulss")), na.rm = TRUE)
  )


```


NOAH participants’ A.) CD4 T-cells/mm3 were ascertained via overnight fasting blood draw at BL, and dichotomized at 500/mm3, generally considered the lower threshold of the normal human range [56]; B.) depression symptomatology was tapped using summed scores of the Hospital Anxiety and Depression Scale 7-item depression subscale (HADS-D). The HADS-D is historically well-validated across contexts, and has demonstrated acceptable sensitivity and specificity for major depression screening in clinical settings. It is scored on a 4-point ordinal scale, with item-specific variations in anchoring [57-58].

```{r CD4 and HADS}


table(noah_filt$cd4cat)
summary(noah_filt$cd4_count)

table(noah_filt$hads_anxietycat)
table(noah_filt$hads_depresscat)


```
	
	
	The (A) control set included race (interpreted as lifecourse racism exposure [49]), recorded in U.S. Census categories; assigned sex; indicators for ART adherence and day-level polysubstance use; and total AUDIT scores, which range from 1–40, with ≥8 suggesting hazardous consumption and ≥15 likely alcohol dependence [58]. The (B) control set included race; assigned sex; reliance on congregate housing, such as homeless shelters; lifetime depression diagnostic markers abstracted from EHR; lifetime economic hardship, scored 1–6 using measures adapted from the U.S. Census Bureau’s Survey of Income and Program Participation; and summed HIV Stigma Scale scores [51].

```{r Controls}

# A Control Set 
table(noah_filt$race)
table(noah_filt$gender)
table(noah_filt$polyusesum)
table(noah_filt$dailypolyuse)
table(noah_filt$auditCAT)

# B Control Set 
table(noah_filt$race)
table(noah_filt$gender)
table(noah_filt$homeless)
table(noah_filt$housing)
summary(noah_filt$lehtotal_sum) # lifetime econ hardship

noah_filt <- noah_filt %>%
  rowwise() %>%
  mutate(stigma_sum = sum(c_across(stigma1:stigma40), na.rm = TRUE)) %>%
  ungroup()

# Check the distribution of the summed stigma scores
summary(noah_filt$stigma_sum)

```

Exploratory factor analysis detected latent subconstructs of urban life stress
I used this documentation as a guide: https://rpubs.com/pjmurphy/758265 

```{r scree-plot, echo=TRUE, fig.width=8, fig.height=6}


# Extract ULSS items with participant ID for tracking
ulss <- noah_filt %>%
  dplyr::select(carc_study_id, ulss1:ulss21)

# Evaluate / Clean Data 
summary(ulss)  # Review missing or non-finite values

ulss_clean <- ulss %>%
  mutate(across(-carc_study_id, ~ ifelse(is.finite(.), ., NA))) %>%
  drop_na()

# Save IDs before dropping for analysis
ulss_ids <- ulss_clean$carc_study_id
ulss_clean <- ulss_clean %>% select(-carc_study_id)

#Kaiser-Meyer-Olkin (KMO) Test for Sampling Adequacy
KMO(ulss_clean)
#Kaiser-Meyer-Olkin factor adequacy
#Call: KMO(r = ulss_clean)
#Overall MSA =  0.91

# Evaluate the correlation Matrix 

cor_matrix <- cor(ulss_clean, use = "pairwise.complete.obs")  # Correlation matrix
view(cor_matrix)
#Don't see any correlations high enough for concern

eigenvalues <- eigen(cor_matrix)$values  # Eigenvalues from the correlation matrix

#Generate a Scree Plot
plot(eigenvalues, 
     type = "b", 
     main = "Scree Plot", 
     xlab = "Number of Factors", 
     ylab = "Eigenvalue", 
     xaxt = "n")  # Suppress default x-axis

#Plot seems to suggest 2? 

# determine the optimal number of factors
fa.parallel(ulss_clean, fa = "fa", n.iter = 100)

#>Parallel analysis suggests that the number of factors =  2  and the number of components =  NA

#Removing the low loading var we discovered after the first run:
ulss_clean <- ulss_clean %>% select(-ulss2, -ulss3, -ulss10, -ulss17)

#Run Factor Analysis w/ 2 factors
fit <- fa(ulss_clean, nfactors = 2, rotate = "promax", fm = "ml")  # Maximum likelihood factor analysis

print(fit, digits = 2, cutoff = 0.3, sort = TRUE)

#Visualize the factor loadings using fa.diagram()
fa.diagram(fit)
# <0.4 variables are:
# ulss2: Job satisf. | ulss3: Raising children | ulss10: marriage/relat. | ulss17: Drugs alc 

#Extract and merge factor scores into the original dataset
factor_scores <- as.data.frame(fit$scores)  # Extract factor scores

# Add the row identifiers for the merge w/ full dataset
ulss_clean <- ulss_clean %>%
  mutate(row_id = row_number())

noah_filt <- noah_filt %>%
  mutate(row_id = row_number())

factor_scores <- factor_scores %>%
  mutate(row_id = ulss_clean$row_id)  

noah_with_scores <- noah_filt %>%
  left_join(factor_scores, by = "row_id")  # Merge factor scores into the original dataset

#Check the final dataset with factor scores
head(noah_with_scores)

# 2 Stressor Factors that embody two different impacts/exposures of structural racism:
#ML 1 seems to be violence: relations with police, relations with racial groups not your own, gang activity  
#ML 2 seems to be more physical environment items: Public services, transportation, housing, alcohol, health(?)

#noah_fi <- noah_with_scores %>% select(-geometry.x, -geometry.y)
#write.csv(noah_fi, 'C:/Users/Ethan/Box/Gentrification PD CD4 Skeen Smith/gent_pat_cd4_61626.csv')
#file corrected for NA obs in obs 67 

```